---
title: "hw01_gapminder"
output: github_document
author: "Liming Liu"
date: '2018-09-13'
---


## Gapminder exploration

Load the `gapminder` R package

```{r}
library(gapminder)
```

Get a quick view of the data

```{r}
head(gapminder)
```
Get a summary of the dataset

```{r}
summary(gapminder)
```


## Explore the column of Asia

Extract the data of Asia and get a summary

```{r}
AsiaData <- gapminder[gapminder$continent=="Asia",]
summary(AsiaData)
```
Extract the data of 2007 and get a ranking according to gdpPercap in 2007

```{r}
Asia2007 <- AsiaData[AsiaData$year==2007,]
Asia2007[rank(Asia2007$gdpPercap),]
```


## Explore the data of a specific country

Extract the data of China and plot the trend of gdpPercap through 1952 - 2007 
 
```{r}
ChinaData <- AsiaData[AsiaData$country=="China",]
plot(ChinaData$year,ChinaData$gdpPercap,lty=1)
```
 
Delete column Continent and Country. Look at the trends between year, lifeExp, pop, gdpPerCap columns

```{r}
ChinaData2 <- ChinaData[,-1]
ChinaData2 <- ChinaData2[,-1]
pairs(ChinaData2)
```


